---
output: github_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```

# stopwords: the R package

[![CRAN Version](https://www.r-pkg.org/badges/version/stopwords)](https://CRAN.R-project.org/package=stopwords)
[![Travis-CI Build Status](https://travis-ci.org/davnn/stopwords.svg?branch=master)](https://travis-ci.org/davnn/stopwords)
[![Downloads](https://cranlogs.r-pkg.org/badges/stopwords)](https://CRAN.R-project.org/package=stopwords)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/stopwords?color=orange)](https://CRAN.R-project.org/package=stopwords)

R package providing "one-stop shopping" for stopword lists in R, for multiple languages and sources.  No longer should text analysis or NLP packages bake in their own stopword lists or functions, since this package can accomodate them all, and is easily extended.

Created by [David Muhr](https://github.com/davnn), and extended in cooperation with [Kenneth Benoit](https://github.com/kbenoit) and [Kohei Watanabe](https://github.com/koheiw).

## Installation

```{r, eval = FALSE}
# from CRAN
install.packages("stopwords")

# Or get the development version from GitHub:
# install.packages("devtools")
devtools::install_github("davnn/stopwords")
```

## Usage

```{r}
head(stopwords::stopwords("de", source = "snowball"), 20)

head(stopwords::stopwords("de", source = "stopwords-iso"), 20)
```

For compability with the former `quanteda::stopwords()`:
```{r}
head(stopwords::stopwords("german"), 20)
```

## Languages available

The following coverage of languages is currently available, by source.  Note that the inclusiveness of the stopword lists will vary by source, and the numebr of languages covered by a stopword list does not necessarily mean that the source is better than one with more limited coverage.  (There may be meany reasons to prefer the "snowball" source over the "stopwords-iso" source, for instance.)

The following languages are currently available:

|	Language	      |	[ISO-639-1 Code](https://en.wikipedia.org/wiki/List_of_ISO_639-1_codes) | `stopwords-iso` | `snowball`	| `SMART`	|	`misc`	|
|:----------------|:--------------:|:---------------:|:----------:|:----------:|:----------:| 								
|	 Afrikaans	|	af	|	✔	|		|		|		|
|	 Arabic	|	ar	|	✔	|		|		|	✔	|
|	 Armenian	|	hy	|	✔	|		|		|		|
|	 Basque	|	eu	|	✔	|		|		|		|
|	 Bengali	|	bn	|	✔	|		|		|		|
|	 Breton	|	br	|	✔	|		|		|		|
|	 Bulgarian	|	bg	|	✔	|		|		|		|
|	 Catalan	|	ca	|	✔	|		|		|	✔	|
|	 Chinese	|	zh	|	✔	|		|		|	✔	|
|	 Croatian	|	hr	|	✔	|		|		|		|
|	 Czech	|	cs	|	✔	|		|		|		|
|	 Danish	|	da	|	✔	|	✔	|		|		|
|	 Dutch	|	nl	|	✔	|	✔	|		|		|
|	 English	|	en	|	✔	|	✔	|	✔	|		|
|	 Esperanto	|	eo	|	✔	|		|		|		|
|	 Estonian	|	et	|	✔	|		|		|		|
|	 Finnish	|	fi	|	✔	|	✔	|		|		|
|	 French	|	fr	|	✔	|	✔	|		|		|
|	 Galician	|	gl	|	✔	|		|		|		|
|	 German	|	de	|	✔	|	✔	|		|		|
|	 Greek	|	el	|	✔	|		|		|	✔	|
|	 Hausa	|	ha	|	✔	|		|		|		|
|	 Hebrew	|	he	|	✔	|		|		|		|
|	 Hindi	|	hi	|	✔	|		|		|		|
|	 Hungarian	|	hu	|	✔	|	✔	|		|		|
|	 Indonesian	|	id	|	✔	|		|		|		|
|	 Irish	|	ga	|	✔	|		|		|		|
|	 Italian	|	it	|	✔	|	✔	|		|		|
|	 Japanese	|	ja	|	✔	|		|		|		|
|	 Korean	|	ko	|	✔	|		|		|		|
|	 Kurdish	|	ku	|	✔	|		|		|		|
|	 Latin	|	la	|	✔	|		|		|		|
|	 Lithuanian	|	lt	|	✔	|		|		|		|
|	 Latvian	|	lv	|	✔	|		|		|		|
|	 Malay	|	ms	|	✔	|		|		|		|
|	 Marathi	|	mr	|	✔	|		|		|		|
|	 Norwegian	|	no	|	✔	|	✔	|		|		|
|	 Persian	|	fa	|	✔	|		|		|		|
|	 Polish	|	pl	|	✔	|		|		|		|
|	 Portuguese	|	pt	|	✔	|	✔	|		|		|
|	 Romanian	|	ro	|	✔	|	✔	|		|		|
|	 Russian	|	ru	|	✔	|	✔	|		|		|
|	 Slovak	|	sk	|	✔	|		|		|		|
|	 Slovenian	|	sl	|	✔	|		|		|		|
|	 Somali	|	so	|	✔	|		|		|		|
|	 Southern Sotho	|	st	|	✔	|		|		|		|
|	 Spanish	|	es	|	✔	|	✔	|		|		|
|	 Swahili	|	sw	|	✔	|		|		|		|
|	 Swedish	|	sv	|	✔	|	✔	|		|		|
|	 Thai	|	th	|	✔	|		|		|		|
|	 Tagalog	|	tl	|	✔	|		|		|		|
|	 Turkish	|	tr	|	✔	|		|		|		|
|	 Ukrainian	|	uk	|	✔	|		|		|		|
|	 Urdu	|	ur	|	✔	|		|		|		|
|	 Vietnamese	|	vi	|	✔	|		|		|		|
|	 Yoruba	|	yo	|	✔	|		|		|		|
|	 Zulu	|	zu	|	✔	|		|		|		|
## Contributing

Additional sources can be defined and contributed by adding new data objects, as follows:

1. **Data object**.  Create a named list of characters, in UTF-8 format, consisting of the stopwords for each language.  The [ISO-639-1](https://en.wikipedia.org/wiki/List_of_ISO_639-1_codes) language code will form the name of the list element, and the values of each element will be the character vector of stopwords for literal matches.  The data object should follow the package naming convention, and be called `data_stopwords_newsource`, where `newsource` is replaced by the name of the new source.

2. **Documentation**.  The new source should be clearly documented, especially the source from which was taken.


## License

This package as well as the source repositories are licensed under MIT.
